Borel regularity for ODEs and Thimble Integrals

### 2023-12-21 exp-resurgence.tex
Update thimble integral proof

\subsubsection{Why does Borel summation work for thimble integrals?}
%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
    \hspace{1cm}
    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}

Let $I_j$ be the thimble integral through the thimble $\Lambda_j$ 

@@

I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu

@@

our main results give an explicit description of $I_j$ as a Laplace transform, and show that $I_j$ is indeed Borel regular. In fact, thimble integrals are Borel regular because they can be turned into Laplace transforms.
\begin{theorem}[see Theorem \ref{thm:thimble_proj_formula-proof}]\label{thm:thimble_proj_formula}
The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
\begin{align}\label{eqn:formula}
\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
\end{align}

@@

@@

@@

The function $I_j$ is Borel regular. More explicitly: \textcolor{orange}{[Try to keep on one line]}

@@

\item As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\phi}_j \defeq \borel_\zeta \tilde{\Phi}_j$ converges near $\zeta=\alpha_j$.
\item If you continue the sum of $\tilde{\phi}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.

@@

In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, they are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$. Generic directions correspond to $\theta\neq \arg (\alpha_k-\alpha_j)$, and $k\neq j$. } Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$. Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha_i-\alpha_j)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).

@@

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
%
\subsubsection{Frequency}\label{transl-freq}
%
The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*B_b & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view. Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}
When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
\begin{align*}
w_b \maps T^*B_b & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{align*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute.
\subsubsection{Boundary}
\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$. When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
\begin{equation}\label{laplace:int}
\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$. We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.

@@

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
for all $\lambda \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$.
Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by 
%
\begin{equation}
    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
\end{equation}
%
Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by

\begin{equation}
    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
\end{equation}

Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$. However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.

@@

Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{a_1,...,a_d\}$. Let $I_j$ be the thimble integral 
\begin{equation}\label{exp-int}
I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
\end{equation}
where $\Lambda_j$ is the thimble through the critical point $a_j$. In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular. The first step will be to rewrite $I_j$ as the Laplace transform of a function $\iota_j$ which is explicitly given by the thimble projection formula \eqref{eqn:formula-proof}.   
\begin{theorem}\label{thm:thimble_proj_formula-proof}
The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
\begin{align}\label{eqn:formula-proof}
\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
\end{align}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{theorem}
\begin{proof}
    Let us recast the integral $I_j$ into the position domain. As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively. Hence, we have
\begin{align*}
I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
\end{align*}
Noticing that the right-hand side is a Laplace transform, we learn that
\begin{equation}\label{thimble-difference}
{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
\end{equation}
\end{proof}
We'll now prove that $I_j$ is Borel regular:
\begin{theorem}\label{thm:maxim-proof}
The function $I_j$ is Borel regular. More explicitly: 
\begin{enumerate}
\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $I_j$.
\end{enumerate}
\end{theorem}
\begin{proof}
    Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$. Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively. We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively. \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.

>>>>

\subsubsection{Why does Borel summation work for thimble integrals?}
%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j^\theta$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j^\theta$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j^\theta$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j^\theta$ can be regarded as the component of $f^{-1}(\Gamma_j^\theta)$ that goes through $a_j$.  \textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
    \hspace{1cm}
    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity along the positive real axis.}
    \label{fig:thimble_vs_rays}
\end{figure}

Let $I_j$ be the thimble integral through the thimble $\Lambda_j^\theta$,

@@

I_j(z)\defeq\int_{\Lambda_j^\theta}e^{-zf}\nu

@@

our main results show that $I_j$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. Thus, we recall the well-known result
\begin{lemma}[see Lemma \ref{lem:thimble_proj_formula-proof}]\label{lem:thimble_proj_formula}
A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}
\begin{equation}\label{eqn:formula}
\iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right),

@@

\end{lemma}

@@

Then, Borel regularity for thimble integrals is stated in the following theorem: 

@@

If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 

@@

\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.

@@

In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$. Generic directions correspond to $\theta\neq \arg (\alpha_k-\alpha_j)$, and $k\neq j$. } Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$. Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha_i-\alpha_j)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).

@@

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
%
\subsubsection{Frequency}\label{transl-freq}
%
The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*B_b & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view. Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}
When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
\begin{align*}
w_b \maps T^*B_b & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{align*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute.
\subsubsection{Boundary}
\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$. When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
\begin{equation}\label{laplace:int}
\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$. We’ll use the shorthand $\laplace_{\zeta, \beta}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = \beta}$ throughout this document.

@@

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
for all $\lambda \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$.
Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
%
\begin{equation}
    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
\end{equation}\color{black}
%
\color{RoyalBlue}Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
%
\begin{equation}
    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
\end{equation}\color{RoyalBlue}
%
Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$. However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}. [Isn't this a special case of the $\laplace_{\zeta, \alpha}$ statement?]\color{black}

@@

Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{a_1,...,a_d\}$. Let $I_j$ be the thimble integral 
\begin{equation}\label{exp-int}
I_j \defeq \int_{\Lambda_j} e^{-zf} \nu
\end{equation}
where $\Lambda_j$ is the thimble through the critical point $a_j$. In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular. The first step will be to rewrite $I_j$ as the Laplace transform of a function $\iota_j$ which is explicitly given by the\textit{thimble projection formula}.% \eqref{eqn:formula-proof}.   
\begin{lemma}\label{lem:thimble_proj_formula-proof}
\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}
\[ \iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right), \]
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{lemma}
\begin{proof}
    Let us recast the integral $I_j$ into the position domain. As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively. Hence, we have
\begin{align*}
I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
\end{align*}
Noticing that the right-hand side is a Laplace transform, we learn that
\begin{equation}\label{thimble-difference}
{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
\end{equation}
\end{proof}
We'll now prove that $I_j$ is Borel regular:
\begin{theorem}\label{thm:maxim-proof}
If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 
\begin{enumerate}
\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.
\end{enumerate}
\end{theorem}
\begin{proof}
Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$. Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively. We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively. \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{m \ge 0} b_m^j \tau^m\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.

Let's write $\approx$ when two functions are asymptotic at all orders around the base poin; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} t  
%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
\[ e^{z \alpha_j} I_j \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
as $z \to \infty$ along the ray $e^{-i\theta}\, \R_{> 0}$. Plugging in the Taylor series for $\nu$, we get
\begin{align*}
e^{z \alpha_j} I_j & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^j \tau^m\,d\tau \\
& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
\end{align*}
By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$. Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!! = 1$.}
\begin{align*}
e^{z \alpha_j} I_j & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
\end{align*}
